\bf Supplement to ``On Devon Allen's Disqualification at the 2022 World Track and Field Championships''

### 2024-11-30 Manuscript/reply.tex
Updated p value from TukeyHSD

We also explored adding data from the 200-meter dash. However, a
generalized gamma model fit to the expanded dataset that included the
200-meter event revealed a significant effect of event type. Tukey’s
Honest Significant Difference (HSD) test found a p-value of 0.0021 for
the 200-meter dash compared to the 110-meter hurdles, and a p-value of
0.000017 for the 100-meter dash compared to the 200-meter dash.
These results indicate that reaction times in the 200-meter dash are
significantly slower. Consequently, we excluded the 200-meter event
from the main analysis, as its systematic differences in reaction
times could bias conclusions about extreme reaction times and the
appropriateness of the 0.1-second threshold.

>>>>

We also explored adding data from the 200-meter dash. However, a
generalized gamma model fit to the expanded dataset that included the
200-meter event revealed a significant effect of event type. Tukey’s
Honest Significant Difference (HSD) test found a p-value of 0.00179 for
the 200-meter dash compared to the 110-meter hurdles, and a p-value of
0.00007 for the 100-meter dash compared to the 200-meter dash.
These results indicate that reaction times in the 200-meter dash are
significantly slower. Consequently, we excluded the 200-meter event
from the main analysis, as its systematic differences in reaction
times could bias conclusions about extreme reaction times and the
appropriateness of the 0.1-second threshold.
